---
title: "esm206 lab 7"
author: "Sarah Lam"
date: "11/9/2021"
output: html_document
---

```{r setup, include= TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Explore penguins

Use `GGally::ggpairs()` to create a pairs plot. 

```{r}
ggpairs(penguins)
```

That's kind of overkill. :et's simplify the variable that we include in our ggpairs plot: 

- species
- bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```

## Multiple linear regression

We are going to try to undersatnd (a bit better) the relationships between multiple predictor variables and an outcome variable which is body mass. 

The different preductor variable we're going to try are: 

- species
- flipper length
- sex
- bill depth 

### Model 1 

Model body mass based on only flopper length and bill depth. 
(bad idea...there are important variables missing.)

```{r}
model_1 <- lm(data = penguins, body_mass_g ~ flipper_length_mm + bill_depth_mm)

model_1 # call model by name to return only the coefficeints

#More information 
summary(model_1)
```

If everything else is held constant, we expect that for each 1mm increase in flipper length, penguin body mass is expected to increae by `r round(model_1$coefficient[2],2)`g, on average. 

R-spqaured interpratatin: 
76% of variance in penguin body mass is explained by this model (containing flipper length and bill depth).

Actually -- we think that a model for penguin body mass should contain variable speices, flipper length, and penguin sex. 
```{r}
model_2 <-  lm(data = penguins, body_mass_g ~ flipper_length_mm + species + sex)

# let's check out the coefficients
model_2

# Try interpretting doefficients for:
# flipper length, Gentoo, and male
```

## Visualize this model 

```{r}
ggplot(data = penguins, aes(flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~sex)
```

## A couple ways to get and report MLR outcomes 

Use broom::tidy() to get model doefficient info in a data frame 

```{r}
penguin_model2_coef <- tidy(model_2)

penguin_model2_coef 
```

Try to write inline code that spits out the coefficient for Gentoo
Gentoo coefficient in model 2 is `r round(penguin_model2_coef$estimate[4], 2)`. 

## Look at model diagnostics 

Use the plot() function. 

```{r}
plot(model_2)

summary(model_2)
```

## Report the model outputs in a summary table

Use modelsummary:
```{r}
modelsummary(model_2)
```

Use stargazer: 
```{r, results = "asis"}
stargazer(model_2, type = "html")
```


